Manuscript

### 2017-10-30 manuscript.Rmd
Updated links to parks datasets.

boston_tracts <- geojson_read("data/boston_tracts.geojson", what = "sp")
boston_parks <- geojson_read("data/boston_parks.geojson", what = "sp")
boston_parks$Park_Acres <- boston_parks$Acreage

nyc_tracts <- geojson_read("data/nyc_tracts.geojson", what = "sp")
nyc_tracts$GEOID10 <- nyc_tracts$GEOID
nyc_tracts$SinglePercent <- nyc_tracts$Single_Percent
nyc_parks <- geojson_read("data/nyc_parks.geojson", what = "sp")

>>>>

boston_tracts <- geojson_read("data/boston_tracts.geojson", what = "sp")
boston_parks <- geojson_read("data/boston_parks_final.geojson", what = "sp")
boston_parks$Park_Acres <- boston_parks$Acreage

nyc_tracts <- geojson_read("data/nyc_tracts.geojson", what = "sp")
nyc_tracts$GEOID10 <- nyc_tracts$GEOID
nyc_tracts$SinglePercent <- nyc_tracts$Single_Percent
nyc_parks <- geojson_read("data/nyc_parks_final.geojson", what = "sp")
